LAGOS lake depth

### 2020-02-06 figures/00_maps.Rmd
rm duplicate labels

gg_states

```

@@

dt_plot <- dt %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::filter(lake_waterarea_ha >= 4) %>%
  group_by(lake_state) %>%
  summarize(prop_maxdepth = mean(!is.na(lake_maxdepth_m))) %>%
  arrange(desc(prop_maxdepth)) %>%
  left_join(dplyr::filter(
    dplyr::select(states_all, postal, iso_a2), iso_a2 == "US"), 
            by = c("lake_state" = "postal")) %>%
  dplyr::filter(!is.na(prop_maxdepth))
st_geometry(dt_plot) <- dt_plot$geom

@@

# limit to lakes with limno data
dt_plot <- dt %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::filter(lake_waterarea_ha >= 4) %>%
  dplyr::filter(has_limno == 1) %>%
  group_by(lake_state) %>%
  summarize(prop_maxdepth = mean(!is.na(lake_maxdepth_m))) %>%
  arrange(desc(prop_maxdepth)) %>%
  left_join(dplyr::filter(
    dplyr::select(states_all, postal, iso_a2), iso_a2 == "US"), 
            by = c("lake_state" = "postal")) %>%
  dplyr::filter(!is.na(prop_maxdepth))
st_geometry(dt_plot) <- dt_plot$geom

ggplot() + 
  geom_sf(data = dt_plot, aes(fill = prop_maxdepth)) + 
  geom_sf_text(data = dt_plot, 
               aes(label = round(prop_maxdepth, 2)), 
               size = 2.5) +
  labs(fill = "") +
  coord_sf(datum = NA) + theme_void()
```

>>>>

gg_states
```

@@

dt_plot <- dt %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::filter(lake_waterarea_ha >= 4) %>%
  group_by(lake_state) %>%
  summarize(prop_maxdepth = mean(!is.na(lake_maxdepth_m))) %>%
  arrange(desc(prop_maxdepth)) %>%
  left_join(dplyr::filter(
    dplyr::select(states_all, postal, iso_a2), iso_a2 == "US"), 
            by = c("lake_state" = "postal")) %>%
  dplyr::filter(!is.na(prop_maxdepth)) %>%
  distinct(lake_state, .keep_all = TRUE)
st_geometry(dt_plot) <- dt_plot$geom

@@

# limit to lakes with limno data
dt_plot <- dt %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  dplyr::filter(lake_waterarea_ha >= 4) %>%
  dplyr::filter(has_limno == 1) %>%
  group_by(lake_state) %>%
  summarize(prop_maxdepth = round(mean(!is.na(lake_maxdepth_m)), 2)) %>%
  arrange(desc(prop_maxdepth)) %>%
  left_join(dplyr::filter(
    dplyr::select(states_all, postal, iso_a2), iso_a2 == "US"), 
            by = c("lake_state" = "postal")) %>%
  dplyr::filter(!is.na(prop_maxdepth)) %>%
  distinct(lake_state, .keep_all = TRUE)
st_geometry(dt_plot) <- dt_plot$geom

ggplot() + 
  geom_sf(data = dt_plot, aes(fill = prop_maxdepth)) + 
  geom_sf_text(data = dt_plot,
               aes(label = prop_maxdepth),
               size = 2.5) +
  labs(fill = "") +
  coord_sf(datum = NA) + theme_void()
```
